---
title: "P8105 homework 3"
author: Yu He
date: 10/14/2021
output: github_document
---

Load packages and dataset
```{r}
library(tidyverse)
library(p8105.datasets)


knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 1,
  out.width = "90%"
)
```

## Problem 1
Description of the dataset

The 'instacart' dataset is the order history of over 3 million online orders collected from more than 200,000 instacart users. The dataset includes `r names(instacart)` variables.

The dataset contains 1,384,617 observations of 131,209 unique users. Each column represent a variable that indicate specific information. The aisle variable represents the name of the aisle, which includes 134 types of items. Among all the items listed in aisle, fresh vegetables, fresh fruits, and packaged vegetables fruits are the top three items ordered through Instacart. Figure in part 2 shows the online order items, which were order more than 10,000 times. The fresh vegetables and fresh fruits were order much more often than all the other items.They are almost the 5 times of the average order time of all the other items. 

```{r}
data("instacart")
```


part 1(a), number of aisels - 134 items

```{r}
instacart_df =
  force(instacart) %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n())
  
```

part 1(b), top 3 items ordered in the aisles - fresh vegetables, fresh fruits, and packaged vegetables fruits.

```{r}
instacart_most_aisle =
  force(instacart) %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  mutate(
    top_order_aisles = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(top_order_aisles > 131)


```

part 2 plot of number of items ordered in each aisles

The fresh vegetables and fresh fruits were order much more often than all the other items. They are almost the 5 times of the average order time of all the other items.

```{r}
instacart_df %>% 
  group_by(aisle) %>% 
  filter(as.numeric(n_obs) > 10000) %>% 
  ggplot(aes(x = n_obs, y = aisle)) +
  geom_point() +
  labs(
    title = "Instacart online items order more than 10,000",
    x = "number of orders",
    y = "item names",
    caption = "Data from The Instacart Online Grocery Shopping Dataset 2017"
  ) 
```

part 3 table of top three product in baking ingredients”, “dog food care”, and “packaged vegetables fruits” listed in aisles.

The packaged vegetables fruits were ordered about ten time more often than other two types of items. Among packaged vegetables fruits, the organic baby spinach was ordered twice more often tha other two types of items.

```{r}
pop_product = 
  instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  select(product_name, aisle) %>% 
  group_by(product_name, aisle) %>% 
  summarize(n_obs = n())

top3_bi = 
  pop_product %>% 
  filter(aisle == "baking ingredients") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 329) %>% 
  select(-prod_rank)

top3_dfc =
  pop_product %>% 
    filter(aisle == "dog food care") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 25) %>% 
  select(-prod_rank)

top3_pvf =
  pop_product %>% 
    filter(aisle == "packaged vegetables fruits") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 4059) %>% 
  select(-prod_rank)

top3_product = bind_rows(top3_bi, top3_dfc, top3_pvf) %>% 
  knitr::kable()

top3_product
```

part 4 table of Pink Lady Apples and Coffee Ice Cream

The average order time of coffee ice cream is higher on Tuesday, Thursday, and Wednesday. And the average order time of pink lady apples is higher on Wednesday, Friday, and Sunday. The order times are closed between coffee ice cream and pink lady apples on Friday and Sunday.

```{r}
apple_cream_df =
  force(instacart) %>% 
  select(order_dow, order_hour_of_day, product_name) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  mutate(order_dow = recode(order_dow, "0" = "Sunday", "1" = "Monday", "2" = "Tuesday", "3" = "Wednesday", "4" = "Thursday", "5" = "Friday", "6" = "Saturday")) %>% 
  group_by(order_dow, product_name) %>% 
  summarize(mean_order_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(names_from = order_dow, values_from = mean_order_hour) %>% 
  knitr::kable()
apple_cream_df

```

## Problem 2

part 1 load, clean and manipulate the BRFSS data

factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))

```{r}
data("brfss_smart2010") 
```

```{r}
health_data_df =
  force(brfss_smart2010) %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Poor", "Fair", "Good", "Very good", "Excellent")) %>% 
  group_by(response) %>% 
  mutate(
    response = factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))
  )
```


part 2(a) states observation in 2002 and 2010

In 2002, 36 states were observed at 7 or more locations. And in 2010, 45 states were observed 7 or more locations. In addition, the figure illustrate us that the states were observed more time in 2010 than in 2002. And FL was observed more than 200 location in 2010. 

```{r}
location_df =
  health_data_df %>% 
  filter(year %in% c("2002", "2010")) %>% 
  group_by(year, locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs > 6) %>% 
  ggplot(aes(x = n_obs, y = locationabbr)) +
  geom_point() +
  facet_wrap(~ year)
location_df
```

part 2(b) plot of average value within a state over time

The overall trend of the average data value within the states is slightly decreased from 2002 to 2010. Some states includes, FL, IL, LA, WY, CA, CT, experience extreme average data value change between 2004 and 2008. Some states includes, ME, MI, MS, MT, NC has relatively stable average data trends. Among these state, WY has the lowest average data value. 

```{r}
state_plot_df =
  health_data_df %>% 
  filter(response == "Excellent") %>% 
  select(year, locationabbr, locationdesc, data_value) %>% 
  group_by(year, locationabbr) %>% 
  summarize(mean_state_value = mean(data_value)) %>% 
  ggplot(aes(x = year, y = mean_state_value, group = locationabbr, color = locationabbr)) +
  geom_line(alpha = .7) +
   viridis::scale_color_viridis(
    name = "States",
    discrete = TRUE
  )

state_plot_df
```

part 2(c) two panel plot from 2006 and 2010 at NY

The observation of response in NY states includes more Good, Very good, and Excellent than Poor and Fair. And we have observed little difference of the overall response between 2006 and 2010. Among counties in NY state, we observed more Very good and Excellent response in Westchester county in 2010. And we observed more Poor to Good response in Bronx county in 2010. However, 2006 has different observations of response. We oberved more Poor and Fair response in Queens county, and more Good to Excellent response in Nassau county.  

```{r}
NY_data_df =
  health_data_df %>% 
  filter(locationabbr == "NY") %>% 
  filter(year %in% c("2006", "2010")) %>% 
  select(year, locationabbr,locationdesc, response, data_value) %>% 
  ggplot(aes(x = response, y = data_value, group = locationdesc, color = locationdesc)) +
  geom_point(alpha = .7) +
  facet_wrap(~ year) +
  labs(
    title = "BRFSS NY state data plot 2006 and 2010",
    caption = "Data from SMART project"
  ) +
  viridis::scale_color_viridis(
    name = "Counties",
    discrete = TRUE
  )
NY_data_df
```

 
## Problem 3

part 1 load and manipulate data
 factor(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))



```{r}
accel_data =
  read_csv("accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    weekday_end = recode(day, "Monday" = "Weekday", "Tuesday" = "Weekday", "Wednesday" = "Weekday", "Thursday" = "Weekday", "Friday" = "Weekday", "Saturday" = "Weekend", "Sunday" = "Weekend")
  ) %>% 
  select(week, day_id, day, weekday_end, everything()) %>% 
  mutate(
    day = ordered(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
  ) 
  
```


  





































