---
title: "P8105 homework 3"
author: Yu He
date: 10/14/2021
output: github_document
---

Load packages and dataset
```{r}
library(tidyverse)
library(p8105.datasets)
data("instacart")

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 1,
  out.width = "90%"
)
```

## Problem 1
Description of the dataset

The 'instacart' dataset is the order history of over 3 million online orders collected from more than 200,000 instacart users. The dataset includes `r names(instacart)`



part 1 a, number of aisels - 134 items

```{r}
instacart_df =
  force(instacart) %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n())
```

part 1 b, top 3 items ordered in the aisles - fresh vegetables, fresh fruits, and packaged vagetables fruits.

```{r}
instacart_most_aisle =
  force(instacart) %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  mutate(
    top_order_aisles = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(top_order_aisles > 131)


```

part 2 plot of number of items ordered in each aisles

```{r}
instacart_df %>% 
  group_by(aisle) %>% 
  filter(as.numeric(n_obs) > 10000) %>% 
  ggplot(aes(x = n_obs, y = aisle)) +
  geom_point() +
  labs(
    title = "Instacart online items order more than 10,000",
    x = "number of orders",
    y = "item names",
    caption = "Data from The Instacart Online Grocery Shopping Dataset 2017"
  ) 
```

part 3 table of top three product in baking ingredients”, “dog food care”, and “packaged vegetables fruits” listed in aisles.

```{r}
pop_product = 
  instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  select(product_name, aisle) %>% 
  group_by(product_name, aisle) %>% 
  summarize(n_obs = n())

top3_bi = 
  pop_product %>% 
  filter(aisle == "baking ingredients") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 329) %>% 
  select(-prod_rank)

top3_dfc =
  pop_product %>% 
    filter(aisle == "dog food care") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 25) %>% 
  select(-prod_rank)

top3_pvf =
  pop_product %>% 
    filter(aisle == "packaged vegetables fruits") %>%
  mutate(
    prod_rank = min_rank(n_obs)
  ) %>% 
  arrange(desc(n_obs)) %>% 
  filter(n_obs > 4059) %>% 
  select(-prod_rank)

top3_product = bind_rows(top3_bi, top3_dfc, top3_pvf) %>% 
  knitr::kable()

top3_product
```

part 4 table of Pink Lady Apples and Coffee Ice Cream

```{r}
apple_cream_df =
  force(instacart) %>% 
  select(order_dow, order_hour_of_day, product_name) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  mutate(order_dow = recode(order_dow, "0" = "Sunday", "1" = "Monday", "2" = "Tuesday", "3" = "Wednesday", "4" = "Thursday", "5" = "Friday", "6" = "Saturday")) %>% 
  group_by(order_dow, product_name) %>% 
  summarize(mean_order_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(names_from = order_dow, values_from = mean_order_hour) %>% 
  knitr::kable()
apple_cream_df

```

## Problem 2

part 1 load, clean and manipulate the BRFSS data

factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent"))

```{r}
data("brfss_smart2010") 
```

```{r}
health_data_df =
  force(brfss_smart2010) %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Poor", "Fair", "Good", "Very good", "Excellent")) %>% 
  group_by(response)  
```


part 2(a) states observation in 2002 and 2010

```{r}
location_df =
  health_data_df %>% 
  filter(year %in% c("2002", "2010")) %>% 
  group_by(year, locationabbr) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs > 6)
```

part 2(b) plot of average value within a state over time

```{r}
state_plot_df =
  health_data_df %>% 
  filter(response == "Excellent") %>% 
  select(year, locationabbr, locationdesc, data_value) %>% 
  group_by(year, locationabbr) %>% 
  summarize(mean_state_value = mean(data_value)) %>% 
  ggplot(aes(x = year, y = mean_state_value, group = locationabbr, color = locationabbr)) +
  geom_line()

state_plot_df
```

part 2(c) two panel plot from 2006 and 2010 at NY, order issue relate to problem 2 part 1

```{r}
NY_data_df =
  health_data_df %>% 
  filter(locationabbr == "NY") %>% 
  filter(year %in% c("2006", "2010")) %>% 
  select(year, locationabbr,locationdesc, response, data_value) %>% 
  ggplot(aes(x = response, y = data_value, group = locationdesc, color = locationdesc)) +
  geom_point() +
  facet_wrap(~ year) +
  labs(
    title = "BRFSS NY state data plot 2006 and 2010",
    caption = "Data from SMART project"
  ) +
  scale_color_hue(name = "NY-counties", h = c(100,300))

NY_data_df
```

 
## Problem 3



  





































